Data preparation

### 2023-04-12 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd
Adding timer and removing function that was moved to oesrrr

```{r}
tictoc::tic()
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!("arsenal" %in% installed.packages()[,"Package"]))
{
  install.packages("arsenal")
}
if(!("oesrrr" %in% installed.packages()[,"Package"]))
{
  devtools::install_github(repo = "GSA/oesrrr")
}
library(oesrrr)
library(tidyverse)
library(janitor)
library(skimr)
library(DataExplorer)
library(readr)
library(arsenal)
library(Hmisc)
library(readxl)
library(flextable)
library(ggthemes)
```

@@

## Functions

Function to display datatable.

```{r}
datatable_with_sampling <- function(in_data, in_max_rows)
{
  if(nrow(in_data) > in_max_rows)
{
  print(glue::glue("Big dataframe. Sampling {scales::comma(in_max_rows)} rows. {Sys.time()}"))
  prep_01 <- 
    in_data %>% 
    sample_n(size = in_max_rows)
}

if(nrow(in_data) <= in_max_rows)
{
  prep_01 <- 
    in_data
}
prep_01 %>% 
  DT::datatable(class = 'cell-border stripe')
}
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
tictoc::tic()
if(!("arsenal" %in% installed.packages()[,"Package"]))
{
  install.packages("arsenal")
}
if(!("oesrrr" %in% installed.packages()[,"Package"]))
{
  devtools::install_github(repo = "GSA/oesrrr")
}
library(oesrrr)
library(tidyverse)
library(janitor)
library(skimr)
library(DataExplorer)
library(readr)
library(arsenal)
library(Hmisc)
library(readxl)
library(flextable)
library(ggthemes)
```

@@
